The Sound of Teaching Music: Expert Pianists' Performance Modulations for Novices

### 2020-12-15 paper/manuscript.Rmd
add kot/kor plots
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

We recruited 21 piano experts who already had a degree in (above bachelor or equivalent) in piano performance/teaching or were studying piano performance at a music school at the time of recruitment. One participant was excluded due to insufficient motor skills (see details in *[Procedure](#procedure-2)*). Twenty participants (`r nrow(dt_2_included[Gender == "Female"])` female) were included in data analysis. Most participants were right-handed (left; `r nrow(dt_2_included[Handedness == "Left"])`). They had `r round(mean(dt_2_included$PianoTotalPractice), 2)` years of practice on average (*SD* = `r round(sd(dt_2_included$PianoTotalPractice), 2)`).

@@

```{r kot-art-2, include = FALSE}
kot_art_plot <- data.table(subject = kot_art[Condition == "teaching"]$SubNr, teaching = kot_art[Condition == "teaching"]$Mean, performing = kot_art[Condition == "performing"]$Mean, subcomponent = kot_art[Condition == "teaching"]$Subcomponent)

kot_art_2 <- ggpaired(kot_art_plot, cond = "performing", cond2 = "teaching", color = "condition", facet.by = "subcomponent", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "KOR", title = "KOR: Articulation") +
  ylim(-1, 0.4) +
  stat_compare_means(label = "p.signif", hide.ns = TRUE, size = 10, label.x = 1.5, label.y = -0.5, paired = TRUE) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

# save plots
ggsave(here("paper/image", "kot_art_2.png"), plot = kot_art_1, dpi = 600, width = 7, height = 5)
img_kot_art_2 <- image_read(here("paper/image", "kot_art_2.png"))
```

@@

```{r kot-dyn-2, include = FALSE}
kot_dyn_plot <- data.table(subject = kot_dyn[Condition == "teaching"]$SubNr, teaching = kot_dyn[Condition == "teaching"]$Mean, performing = kot_dyn[Condition == "performing"]$Mean, subcomponent = kot_dyn[Condition == "teaching"]$Subcomponent)

kot_dyn_2 <- ggpaired(kot_dyn_plot, cond = "performing", cond2 = "teaching", color = "condition", facet.by = "subcomponent", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "KOR", title = "KOR: Dynamics") +
  ylim(-1, 0.4) +
  stat_compare_means(label = "p.signif", hide.ns = TRUE, size = 10, label.x = 1.5, label.y = -0.5, paired = TRUE) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

# save plots
ggsave(here("paper/image", "kot_dyn_2.png"), plot = kot_dyn_1, dpi = 600, width = 7, height = 5)
img_kot_dyn_2 <- image_read(here("paper/image", "kot_dyn_2.png"))
```

## 3.4. Discussion

>>>>

We recruited 21 piano experts who already had a degree in (above bachelor or equivalent) in piano performance/teaching or were studying piano performance at a music school at the time of recruitment. For data analysis, we excluded 1 participants due to insufficient motor skills (1) and an overall deviated tempo (1). Nineteen participants (`r nrow(dt_2_included[Gender == "Female"])` female) were included in data analysis. Most participants were right-handed (left; `r nrow(dt_2_included[Handedness == "Left"])`). They had `r round(mean(dt_2_included$PianoTotalPractice), 2)` years of practice on average (*SD* = `r round(sd(dt_2_included$PianoTotalPractice), 2)`).

@@

```{r kor-art-2, include = FALSE}
kor_art_plot <- data.table(subject = kor_art[Condition == "teaching"]$SubNr, teaching = kor_art[Condition == "teaching"]$Mean, performing = kor_art[Condition == "performing"]$Mean, subcomponent = kor_art[Condition == "teaching"]$Subcomponent)

kor_art_2 <- ggpaired(kor_art_plot, cond = "performing", cond2 = "teaching", color = "condition", facet.by = "subcomponent", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "KOR", title = "KOR: Articulation") +
  ylim(-1, 0.4) +
  stat_compare_means(label = "p.signif", hide.ns = TRUE, size = 10, label.x = 1.5, label.y = -0.5, paired = TRUE) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

# save plots
ggsave(here("paper/image", "kor_art_2.png"), plot = kor_art_2, dpi = 600, width = 7, height = 5)
img_kor_art_2 <- image_read(here("paper/image", "kor_art_2.png"))
```

@@

```{r kor-dyn-2, include = FALSE}
kor_dyn_plot <- data.table(subject = kor_dyn[Condition == "teaching"]$SubNr, teaching = kor_dyn[Condition == "teaching"]$Mean, performing = kor_dyn[Condition == "performing"]$Mean, subcomponent = kor_dyn[Condition == "teaching"]$Subcomponent)

kor_dyn_2 <- ggpaired(kor_dyn_plot, cond = "performing", cond2 = "teaching", color = "condition", facet.by = "subcomponent", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "KOR", title = "KOR: Dynamics") +
  ylim(-1, 0.4) +
  stat_compare_means(label = "p.signif", hide.ns = TRUE, size = 10, label.x = 1.5, label.y = -0.5, paired = TRUE) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

# save plots
ggsave(here("paper/image", "kor_dyn_2.png"), plot = kor_dyn_2, dpi = 600, width = 7, height = 5)
img_kor_dyn_2 <- image_read(here("paper/image", "kor_dyn_2.png"))
```

```{r plot-kot-2, out.width = "100%", fig.cap = "\\label{fig:kot-2}Experiment 2: KOR when playing the piece with either articulation (left) or dynamics (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box. Significance levels: * \\textit{p} < .05, ** \\textit{p} < .01, *** \\textit{p} < .001"}
# combine
img_kor_2 <- image_append(c(img_kor_art_2, img_kor_dyn_2))
image_write(img_kor_2, path = here("paper/image", "img_kor_2.png"), format = "png")
img_kor_2
```
## 3.4. Discussion

### 2020-12-15 paper/manuscript.tex
add kot/kor plots
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

We recruited 21 piano experts who already had a degree in (above bachelor or equivalent) in piano performance/teaching or were studying piano performance at a music school at the time of recruitment. One participant was excluded due to insufficient motor skills (see details in \emph{\protect\hyperlink{procedure-2}{Procedure}}). Twenty participants (9 female) were included in data analysis. Most participants were right-handed (left; 2). They had 15.65 years of practice on average (\emph{SD} = 5.67).

@@

>>>>

We recruited 21 piano experts who already had a degree in (above bachelor or equivalent) in piano performance/teaching or were studying piano performance at a music school at the time of recruitment. For data analysis, we excluded 1 participants due to insufficient motor skills (1) and an overall deviated tempo (1). Nineteen participants (9 female) were included in data analysis. Most participants were right-handed (left; 2). They had 15.65 years of practice on average (\emph{SD} = 5.67).

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-kot-2-1} \caption{\label{fig:kot-1}Experiment 2: KOR when playing the piece with either articulation (left) or dynamics (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box. Significance levels: * \textit{p} < .05, ** \textit{p} < .01, *** \textit{p} < .001}\label{fig:plot-kot-2}
\end{figure}
